\Large \bf 6.829 Final Project: A comparison of bit-rate selection algorithms

### 2013-05-16 paper/paper.tex
Line breaks.

This paper will provide a general overview of SampleRate and Minstrel. We then discuss our testing methodology. We compare the performance of the two algorithms, and then discuss modifications we made to Minstrel and compare it's performance to the current kernel implementation.
\section{SampleRate}

@@

\section{Acknowledgments}
We would like to thank Jonathan Perry and Hari Balakrishnan for their valuable guidance, as well as Derek Smithies for answering our questions about Minstrel.

>>>>

This paper will provide a general overview of SampleRate and
Minstrel. We then discuss our testing methodology. We compare the
performance of the two algorithms, and then discuss modifications we
made to Minstrel and compare it's performance to the current kernel
implementation.

\section{SampleRate}

@@

\section{Acknowledgments}

We would like to thank Jonathan Perry and Hari Balakrishnan for their
valuable guidance, as well as Derek Smithies for answering our
questions about Minstrel.
